Digital History in Finland, 1488-1828

### 2016-06-22 inst/examples/manuscript-krakow.Rmd
Rmd update

## Introduction

@@

Embed citations from bib files with `r citep(bib[["lahti14natcomm"]])`.

@@

>>>>

## Introduction (MT + JM voi jo kasata tähän hyvää läppää + viitteitä)

@@

@@

You can also add citations by adding new references to the [bib
file](bibliography.bib) and then citing in this text with
`r citep(bib[["lahti14natcomm"]])`. These will then be automatically
numbered and collected in references section. Alternatively, you can cite with the DOI (the citation info will then be collected automatically): `r citep("10.18352/lq.10112")`.
